\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-09-14 sections/results.tex
Update on Overleaf.

  We developed \ac{micone}, a flexible and modular pipeline for the inference of co-occurrence networks from 16S data.
  \ac{micone} incorporates various popular, publicly available tools as well as custom Python modules for 16S data analysis and network inference (see Methods).
  The different steps that are a part of the \ac{micone} co-occurrence network inference workflow (Figure~\ref{fig:figure1}) can be grouped into five major modules; (i) sequence processing (SP); (ii) denoising and clustering (DC); (iii) taxonomy assignment (TA); (iv) \ac{otu} processing (OP); (v) network inferences (NI).
  Each process in the pipeline can be implemented through  multiple tools (see Methods and Figure~\ref{fig:figure1}).
  The effects of changing any intermediate step of the pipeline can be evaluated in terms of the final network outcome, as well as on any of the intermediate metrics and data outputs.
  The choice of tools and parameters is encoded in a configuration file (with defaults shown in Tables S2-S6 at \href{https://github.com/segrelab/MiCoNE-pipeline-paper}{https://github.com/segrelab/MiCoNE-pipeline-paper}).
  Through a systematic analysis of tool combinations at each step of the pipeline, we estimated how much the final co-occurrence network depends on the possible choices at each step.

@@

  The systematic analyses in the previous sections illustrate that the choice of tools and parameters can have a big impact on the final consensus co-occurrence network.
  However, the mock communities and synthetic data provide an opportunity to select combinations of tools that yield accurate and robust results.
  As highlighted in the above sections for individual steps, we propose a set of tools and parameters as the defaults for the pipeline (Table~\ref{tab:micone_tools}).

  Figure~\ref{fig:figure7}A shows the comparison of this default network against networks generated by altering one of the steps of the pipeline relative to the default.
  This result suggests that the most significant changes occur when the \ac{ta} step, \ac{op} step, and the \ac{ni} step are changed.
  However, the L1 distance (see Methods) between networks generated by altering one of the steps and the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ni} step is changed from the consensus algorithm to one of the individual algorithms.
  % TODO: Update this and the corresponding figure
  XXXXXXXX Notably, despite the overall big effect of the TA database on the whole pipeline, this choice does not , but the edges between the common nodes (with the default network) are fairly conserved.

  The low L1 distances show us that not only does the consensus help reconcile the variability in the edges due to multiple network inference algorithms, but it also helps reduce the variability due to the other steps of the pipeline as well.
  This result is different from that observed in Figure~\ref{fig:figure6} since in this particular analysis all the steps other than the \ac{ni} step have the consensus algorithm applied to them, which drastically reduces the edges in the graph that have lower probabilities.
  This reinforces the importance of the consensus network in increasing the robustness of the inferred networks to change in processing methods.

>>>>

  We developed \ac{micone}, a flexible and modular pipeline for the inference of co-occurrence networks from 16S data.
  \ac{micone} incorporates various popular, publicly available tools as well as custom Python modules for 16S data analysis and network inference (see Methods).
  The different steps that are a part of the \ac{micone} co-occurrence network inference workflow (Figure~\ref{fig:figure1}) can be grouped into five major modules; (i) \ac{sp}; (ii) \ac{dc}; (iii) \ac{ta}; (iv) \ac{op}; (v) \ac{ni}.
  Each process in the pipeline can be implemented through  multiple tools (see Methods and Figure~\ref{fig:figure1}).
  The effects of changing any intermediate step of the pipeline can be evaluated in terms of the final network outcome, as well as on any of the intermediate metrics and data outputs.
  The choice of tools and parameters is encoded in a configuration file (with defaults shown in Tables S2-S6 at \href{https://github.com/segrelab/MiCoNE-pipeline-paper}{https://github.com/segrelab/MiCoNE-pipeline-paper}).
  Through a systematic analysis of tool combinations at each step of the pipeline, we estimated how much the final co-occurrence network depends on the possible choices at each step.

@@

  The systematic analyses in the previous sections illustrate that the choice of tools and parameters can have a big impact on the final consensus co-occurrence network.
  However, the mock communities and synthetic data provide an opportunity to select combinations of tools that yield the most accurate and robust results.
  As highlighted in the above sections for individual steps, we propose a set of tools and parameters as the defaults for the pipeline (Table~\ref{tab:micone_tools}).

  [REVISIT THIS PART]
  Figure~\ref{fig:figure7} shows the comparison of this default network against networks generated by altering one of the steps of the pipeline relative to the default.
  This result, both visually (Figure~\ref{fig:figure7}A), and quantitatively (Figure~\ref{fig:figure7}B)  suggests that the most significant changes occur when the \ac{ta} step and the \ac{op} changed.
  Notably, however despite the overall big effect of the TA database on the whole pipeline, the edges between the common nodes (with the default network) are fairly conserved, suggesting that the pipeline, with the consensus network at the end, provides a robust avenue for inferring associations.
